SI

### 2021-05-07 ms/si.Rmd
Update SI
remove minor gridlines
fix generation / life stage

**Title:** Intergenerational niche differentiation in filmy ferns (Hymenophyllaceae)

@@

**Corresponding author:** Joel H. Nitta  
Department of Integrated Biosciences, Graduate School of Frontier Sciences, The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8562, Japan  
Phone: +81-4-7136-3681  
Fax: +81-4-7136-3680  
email: joelnitta\\@gmail.com
")
```

@@

# Combine plots
licl_temp_plot_2012 + licl_temp_plot_2013 + licl_temp_plot_2014 +
  licl_rh_plot_2012 + licl_rh_plot_2013 + licl_rh_plot_2014 +
  licl_time_plot_2012 + licl_time_plot_2013 + licl_time_plot_2014 +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "**a**") &
  theme(plot.title = element_markdown())
```

@@

# Combine plots
mgno3_temp_plot_2012 + mgno3_temp_plot_2013 + mgno3_temp_plot_2014 +
  mgno3_rh_plot_2012 + mgno3_rh_plot_2013 + mgno3_rh_plot_2014 +
  mgno3_time_plot_2012 + mgno3_time_plot_2013 + mgno3_time_plot_2014 +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "**b**") &
  theme(plot.title = element_markdown())
```

@@

# Combine plots
nacl_temp_plot_2012 + nacl_temp_plot_2013 + nacl_temp_plot_2014 +
  nacl_rh_plot_2012 + nacl_rh_plot_2013 + nacl_rh_plot_2014 +
  nacl_time_plot_2012 + nacl_time_plot_2013 + nacl_time_plot_2014 +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "**c**") &
  theme(
    plot.title = element_markdown(),
    legend.position = "bottom")
```

@@

# Combine into final plot
chamber_gameto_2012_temp_plot + chamber_gameto_2013_temp_plot +
  chamber_gameto_2012_rh_plot + chamber_gameto_2013_rh_plot + 
  dt_times_gameto_2012_plot + dt_times_gameto_2013_plot + 
  plot_layout(ncol = 2, nrow = 3) +
  plot_annotation(title = "**d**") &
  theme(plot.title = element_markdown())
```

@@

ggplot(rel_water_species_means_with_rec, aes(x = rec_time, y = rel_water, group = interaction(dry_time, salt))) +
  geom_errorbar(
    aes(ymin = rel_water - sd, ymax = rel_water + sd),
    color = "grey50",
    width = 0,
    position = pd) +
  geom_line(position = pd, aes(linetype = dry_time), color = "grey30") +
  geom_point(aes(shape = salt, fill = salt), position = pd) +
  scale_linetype_manual(name = "Desiccation time",
                        values = c("solid", "dashed"),
                        breaks = c("15", "2"),
                        labels = c("15 days", "2 days")) +
  scale_shape_manual(name = "Desiccation intensity",
                     values = salt_shapes,
                     breaks = c("NaCl", "MgNO3",  "LiCl", "Control"),
                     labels = c("-38 MPa", "-86 MPa", "-282 Mpa", "Control")) + 
  scale_fill_manual(name = "Desiccation intensity",
                    values = salt_cols, 
                    breaks = c("NaCl", "MgNO3",  "LiCl", "Control"),
                    labels = c("-38 MPa", "-86 MPa", "-282 Mpa", "Control")) +
  scale_y_continuous(label = scales::percent) +
  facet_wrap(vars(species)) +
  labs(x = "Condition",
       y = "Relative water content") +
  theme_bw() +
  theme(
    panel.grid.major.x = element_blank(),
    strip.text = element_markdown(),
    legend.position = "bottom",
    legend.box="vertical", 
    legend.margin=margin()
  )
```

@@

  ggplot(data, 
         aes(x = habit, y = {{var_name}}, fill = generation)) +
    geom_boxplot(outlier.size = 0) +
    geom_point(pch = 21, position = position_jitterdodge(jitter.width = 0.2)) +
    scale_fill_manual(values = generation_colors, labels = str_to_sentence) +
    labs(
      y = var_label,
      x = "Growth Habit",
      fill = "Generation"
    )

@@

a + b + c + guide_area() + 
  plot_layout(ncol = 2, guides = 'collect') + 
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(face = 'bold'))
```

>>>>

**Title:** Ecophysiological differentiation between life stages in filmy ferns (Hymenophyllaceae)

@@

**Corresponding author:** Joel H. Nitta  
Department of Biological Sciences, Graduate School of Science, The University of Tokyo, 2-11-16 Yayoi, Bunkyo-ku, Tokyo 113-0032, Japan  
Phone: +81-4-7136-3681  
Fax: +81-4-7136-3680  
email: joelnitta\\@gmail.com
")
```

@@

# Combine plots
licl_temp_plot_2012 + licl_temp_plot_2013 + licl_temp_plot_2014 +
  licl_rh_plot_2012 + licl_rh_plot_2013 + licl_rh_plot_2014 +
  licl_time_plot_2012 + licl_time_plot_2013 + licl_time_plot_2014 +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "**a**") &
  theme(plot.title = element_markdown(), panel.grid.minor = element_blank())
```

@@

# Combine plots
mgno3_temp_plot_2012 + mgno3_temp_plot_2013 + mgno3_temp_plot_2014 +
  mgno3_rh_plot_2012 + mgno3_rh_plot_2013 + mgno3_rh_plot_2014 +
  mgno3_time_plot_2012 + mgno3_time_plot_2013 + mgno3_time_plot_2014 +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "**b**") &
  theme(plot.title = element_markdown(), panel.grid.minor = element_blank())
```

@@

# Combine plots
nacl_temp_plot_2012 + nacl_temp_plot_2013 + nacl_temp_plot_2014 +
  nacl_rh_plot_2012 + nacl_rh_plot_2013 + nacl_rh_plot_2014 +
  nacl_time_plot_2012 + nacl_time_plot_2013 + nacl_time_plot_2014 +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "**c**") &
  theme(
    plot.title = element_markdown(),
    legend.position = "bottom",
    panel.grid.minor = element_blank()
  )
```

@@

# Combine into final plot
chamber_gameto_2012_temp_plot + chamber_gameto_2013_temp_plot +
  chamber_gameto_2012_rh_plot + chamber_gameto_2013_rh_plot + 
  dt_times_gameto_2012_plot + dt_times_gameto_2013_plot + 
  plot_layout(ncol = 2, nrow = 3) +
  plot_annotation(title = "**d**") &
  theme(plot.title = element_markdown(), panel.grid.minor = element_blank())
```

@@

ggplot(rel_water_species_means_with_rec, aes(x = rec_time, y = rel_water, group = interaction(dry_time, salt))) +
  geom_errorbar(
    aes(ymin = rel_water - sd, ymax = rel_water + sd),
    color = "grey50",
    width = 0,
    position = pd) +
  geom_line(position = pd, aes(linetype = dry_time), color = "grey30") +
  geom_point(aes(shape = salt, fill = salt), position = pd) +
  scale_linetype_manual(name = "Desiccation time",
                        values = c("solid", "dashed"),
                        breaks = c("15", "2"),
                        labels = c("15 days", "2 days")) +
  scale_shape_manual(name = "Desiccation intensity",
                     values = salt_shapes,
                     breaks = c("NaCl", "MgNO3",  "LiCl", "Control"),
                     labels = c("-38 MPa", "-86 MPa", "-282 Mpa", "Control")) + 
  scale_fill_manual(name = "Desiccation intensity",
                    values = salt_cols, 
                    breaks = c("NaCl", "MgNO3",  "LiCl", "Control"),
                    labels = c("-38 MPa", "-86 MPa", "-282 Mpa", "Control")) +
  scale_y_continuous(label = scales::percent) +
  facet_wrap(vars(species)) +
  labs(x = "Condition",
       y = "Relative water content") +
  theme_bw() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_markdown(),
    legend.position = "bottom",
    legend.box="vertical", 
    legend.margin=margin()
  )
```

@@

  ggplot(data, 
         aes(x = habit, y = {{var_name}}, fill = generation)) +
    geom_boxplot(outlier.size = 0) +
    geom_point(pch = 21, position = position_jitterdodge(jitter.width = 0.2)) +
    scale_fill_manual(values = generation_colors, labels = str_to_sentence) +
    labs(
      y = var_label,
      x = "Growth Habit",
      fill = "Life stage"
    )

@@

a + b + c + guide_area() + 
  plot_layout(ncol = 2, guides = 'collect') + 
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(face = 'bold'), panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank())
```
